Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-07-04 WSSSPE2_report/WSSSPE2_review.tex
Bigger font size but still smaller than regular to make text more readable.
Sections 8-10: Technical report titles do not need first letter capital.

\begin{table*}[ht]
 \centering
\caption{Enablers of software sustainability, with 0 to 10 `*'s roughly
indicating the fraction of attendees who voted for an item as important.}
\label{tb:software_sustainability_enablers}
  \begin{scriptsize}
  \begin{tabular}{ | p{1.65cm} | p{10.0cm} |}
   %  \begin{tabular}{ | p{1.9cm} | p{11.5cm} |}
    \hline
  Importance & Item \\ \hline \hline
********** & healthy and vibrant communities; vibrant community to champion software \\ \hline
********** & designing for growth and extension -- open development \\ \hline
******* & culture in community for reuse \\ \hline
**** & portability \\ \hline
**** & culture in development community to support transition between developers \\ \hline
*** & interdisciplinary people: science + IT experience \\ \hline
** & planning for end of life \\ \hline
** & make smart choices about dependencies \\ \hline
* & thinking of software as product lines -- long term vs.~short term view \\ \hline
 & not all communities need new software \\ \hline
 & converting use into resources \\ \hline
    \end{tabular}
    \end{scriptsize}
\end{table*}

\begin{table}[ht]
\caption{Barriers to software sustainability, with 0 to 10 `*'s roughly
indicating the fraction of attendees who voted for an item as important.}
\label{tb:software_sustainability_barriers}
 \centering
  \begin{scriptsize}
  \begin{tabular}{ | p{1.65cm} | p{10.0cm} |}
% \begin{tabular}{ | p{1.9cm} | p{11.5cm} |}
   \hline
  Importance & Item \\ \hline \hline
******* & lack of incentives, including promotion and tenure process; promotion
and tenure process in academic is incompatible with sustainability \\ \hline
*****  & absent or poor documentation \\ \hline
***** & funding to ensure sustainability is difficult to obtain \\ \hline
**** & developers are not computer scientists; don't have software engineering
practices (in particular, those needed to scale-up projects to support and be
developed by a large sustainable community) \\ \hline
*** & overreliance on one or two people -- the `bus test'\footnote{``Bus test''
in Table~\ref{tb:software_sustainability_barriers} refers to the smallest number
of key people a project would need to lose to become non-viable (the larger the
number, the healthier the project).} \\ \hline
** & rate of change of underlying technologies \\ \hline
** & lack of business models for sustainability \\ \hline
* & lack of training for how to build sustainability into the system \\ \hline
 & maintenance for software is not visible, appears to ``just happen'' \\ \hline
 & licensing issues \\ \hline
 & staff turnover -- lack of continuity \\ \hline
\end{tabular}
 \end{scriptsize}
\end{table}

@@

\item Daniel S. Katz and Arfon M. Smith. Implementing Transitive Credit with
{JSON-LD}~\cite{wssspe2_katz}

@@

%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\subsection{Papers}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
The papers that were discussed in the Reproducibility \& Reuse \& Sharing group are:
\begin{itemize}
\item Jakob Blomer, Dario Berzano, Predrag Buncic, Ioannis Charalampidis,
Gerardo Ganis, George Lestaris and Ren\'{e} Meusel. The Need for a Versioned
Data Analysis Software Environment~\cite{wssspe2_blomer}

\item Ryan Chamberlain and Jennifer Schommer. Using {Docker} to Support
Reproducible Research~\cite{wssspe2_chamberlain}

@@

\item Tom Crick, Benjamin A. Hall, and Samin Ishtiaq. ``Can I Implement Your
Algorithm?'': A Model for Reproducible Research Software~\cite{wssspe2_crick}

\item Bryan Marker, Don Batory, Field G. Van Zee, and Robert van de Geijn. Making
Scientific Computing Libraries Forward Compatible~\cite{wssspe2_marker}

\item Stephen Piccolo. Building Portable Analytical Environments to improve
sustainability of computational-analysis pipelines in the
sciences~\cite{wssspe2_piccolo}
\end{itemize}

@@

The papers that were discussed in the Code Testing \& Code Review group are:
\begin{itemize}
\item Thomas Clune, Michael Rilee, and Damian Rouson. Testing as an Essential
Process for Developing and Maintaining Scientific Software~\cite{wssspe2_clune}

\item Marian Petre and Greg Wilson. Code Review For and By
Scientists~\cite{wssspe2_petre}

\item Andrew E. Slaughter, Derek R. Gaston, John Peterson, Cody J. Permann,
David Andrs, and Jason M. Miller. Continuous Integration for Concurrent {MOOSE}
Framework and Application Development on {GitHub}~\cite{wssspe2_slaughter}
\end{itemize}

>>>>

\begin{table*}[ht]
\centering
\caption{Enablers of software sustainability, with 0 to 10 `*'s roughly
indicating the fraction of attendees who voted for an item as important.}
\label{tb:software_sustainability_enablers}
  \begin{small}
  \begin{tabular}{ | p{1.65cm} | p{12.0cm} |}
   %  \begin{tabular}{ | p{1.9cm} | p{11.5cm} |}
    \hline
  Importance & Item \\ \hline \hline
********** & healthy and vibrant communities; vibrant community to champion software \\ \hline
********** & designing for growth and extension -- open development \\ \hline
******* & culture in community for reuse \\ \hline
**** & portability \\ \hline
**** & culture in development community to support transition between developers \\ \hline
*** & interdisciplinary people: science + IT experience \\ \hline
** & planning for end of life \\ \hline
** & make smart choices about dependencies \\ \hline
* & thinking of software as product lines -- long term vs.~short term view \\ \hline
 & not all communities need new software \\ \hline
 & converting use into resources \\ \hline
    \end{tabular}
    \end{small}
\end{table*}

\begin{table}[ht]
\caption{Barriers to software sustainability, with 0 to 10 `*'s roughly
indicating the fraction of attendees who voted for an item as important.}
\label{tb:software_sustainability_barriers}
 \centering
  \begin{small}
  \begin{tabular}{ | p{1.65cm} | p{12.0cm} |}
% \begin{tabular}{ | p{1.9cm} | p{11.5cm} |}
   \hline
  Importance & Item \\ \hline \hline
******* & lack of incentives, including promotion and tenure process; promotion
and tenure process in academic is incompatible with sustainability \\ \hline
*****  & absent or poor documentation \\ \hline
***** & funding to ensure sustainability is difficult to obtain \\ \hline
**** & developers are not computer scientists; don't have software engineering
practices (in particular, those needed to scale-up projects to support and be
developed by a large sustainable community) \\ \hline
*** & overreliance on one or two people -- the `bus test'\footnote{``Bus test''
in Table~\ref{tb:software_sustainability_barriers} refers to the smallest number
of key people a project would need to lose to become non-viable (the larger the
number, the healthier the project).} \\ \hline
** & rate of change of underlying technologies \\ \hline
** & lack of business models for sustainability \\ \hline
* & lack of training for how to build sustainability into the system \\ \hline
 & maintenance for software is not visible, appears to ``just happen'' \\ \hline
 & licensing issues \\ \hline
 & staff turnover -- lack of continuity \\ \hline
\end{tabular}
 \end{small}
\end{table}

@@

\item Daniel S. Katz and Arfon M. Smith. Implementing transitive credit with
{JSON-LD}~\cite{wssspe2_katz}

@@

%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\subsection{Papers}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
The papers that were discussed in the Reproducibility \& Reuse \& Sharing group are:
\begin{itemize}
\item Jakob Blomer, Dario Berzano, Predrag Buncic, Ioannis Charalampidis,
Gerardo Ganis, George Lestaris and Ren\'{e} Meusel. The need for a versioned
data analysis software environment~\cite{wssspe2_blomer}

\item Ryan Chamberlain and Jennifer Schommer. Using {Docker} to support
reproducible research~\cite{wssspe2_chamberlain}

@@

\item Tom Crick, Benjamin A. Hall, and Samin Ishtiaq. ``Can I implement your
algorithm?'': A model for reproducible research software~\cite{wssspe2_crick}

\item Bryan Marker, Don Batory, Field G. Van Zee, and Robert van de Geijn. Making
scientific computing libraries forward compatible~\cite{wssspe2_marker}

\item Stephen Piccolo. Building portable analytical environments to improve
sustainability of computational-analysis pipelines in the
sciences~\cite{wssspe2_piccolo}
\end{itemize}

@@

The papers that were discussed in the Code Testing \& Code Review group are:
\begin{itemize}
\item Thomas Clune, Michael Rilee, and Damian Rouson. Testing as an essential
process for developing and maintaining scientific software~\cite{wssspe2_clune}

\item Marian Petre and Greg Wilson. Code review for and by
scientists~\cite{wssspe2_petre}

\item Andrew E. Slaughter, Derek R. Gaston, John Peterson, Cody J. Permann,
David Andrs, and Jason M. Miller. Continuous integration for concurrent {MOOSE}
framework and application development on {GitHub}~\cite{wssspe2_slaughter}
\end{itemize}
